%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  


% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
% Increase text height
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage{dirtytalk}
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Md. Saif Hassan Onim}


\address{Graduate Research and Teaching Assistant, Department of EECS,
University of Tennessee, Knoxville, USA\\\hfil
Email: monim@vols.utk.edu, onim.hassan16@gmail.com\\\hfil
\href{https://www.linkedin.com/in/md-saif-hassan-onim-83516b179/}{\textbf{[LinkedIn]}} \quad \href{https://www.researchgate.net/profile/Md_Saif_Onim}{\textbf{[Researchgate]}} \quad \href{https://scholar.google.com/citations?hl=en\&user=BhVJmUcAAAAJ}{\textbf{[Google Scholar]}} \quad \href{https://sites.google.com/view/md-saif-hassan/}{\textbf{[Personal Site]}} }\hfil

\begin{resume}


\section{EDUCATION}
\begin{itemize}
\item \bf{University of Tennessee, Knoxville}, TN-37916, USA\\
\sl PhD in Computer Engineering\\
\sl GPA \bf 4.00/4.00 (current)\\
\textbf {2022--Ongoing}
\item \bf{Military Institute of Science and Technology}, Dhaka-1216, BD\\
\sl Bachelor of Science in Electrical, Electronic and Communication Engineering\\
\sl CGPA \bf 3.72/4.00\\
\textbf {2016-2020}\\
\sl Graduation: \bf January,2020.
% \item \bf{Shahid Syed Nazrul Islam College}, Mymensingh-2201, BD\\
% \sl Higher Secondary-School Certificate in Science\\
% \sl GPA \bf 5.00/5.00\\
% \textbf {2013-2015}\\
% \sl Graduation: \bf August,2015.


\end{itemize}

\section{RESEARCH\\INTERESTS}
\begin{itemize}
\item \bf Machine Learning, \bf Computer Vision, \bf Deep Learning, \bf Image Segmentation, \bf TinyML, \bf Stress Detection, \bf Wearable Devices, \bf Embedded Systems, \bf Quantum Machine Learning
\end{itemize}

\section{MAJOR\\ACADEMIC\\COURSES}
\begin{itemize}
\item \bf Machine Learning and Neural Networks,
\bf Cloud and Edge Computing,
\bf Random Signals Processing,
\bf Computer Programming,
\bf Adversarial Machine Learning,
\bf Natural Language Processing,
\bf Embedded Systems
\end{itemize}


\section{PROGRAMMING\\SKILLS\\\textbf{[Level: Advanced]}}
\begin{itemize}
\item \textbf{Programming Languages:} Python, Matlab , C, LaTeX, Assembly, Verilog. \textbf{Deep-learning and Computer Vision Library:} Keras, Pytorch, Tensorflow, OpenCV. \textbf{Design Tools:} Proteus, Emu8086 (Intel), Keil (AMD), ORCADE PSPICE, Quartus. \textbf{Hardware:} Multi-layer PCB designing, FPGA. \textbf{Graphics:} AUTOCAD, Adobe XD. \textbf{Networking:} CISCO Packet Tracer. \textbf{Operating System:} Windows, Linux (UBUNTU).
\end{itemize}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------

\section{PUBLICATIONS}
\subsection{Posters}
\begin{itemize}

\item \textbf{Md. Saif Hassan Onim} and Himanshu Thapliyal, \say{Performance of Quantum Hybrid Support Vector Machine in Stress Detection,} \textit{Quantum Computing User Forum, 2024, ORNL, Knoxville, TN, USA, August 12-15, \textbf{2024}}

\item Elizabeth K. Rhodus, \textbf{Md. Saif hassan Onim}, Celeste Roberts, Sanjeev Kumar, Amer M Burhan, and Himanshu Thapliyal, \say{Utilization of Wearable Devices as Means for Remote Digital Biometric Data Collection in a Community-based, Rural Randomized Controlled Trial Among Alzheimer’s Disease Dyads,} \textit{in Alzheimer’s Association International Conference. ALZ, \textbf{2024}}

\item Himanshu Thapliyal and \textbf{Md. Saif Hassan Onim},\say{Predicting Psychological and Physiological Stress with Biomarkers and Wearable Sensors}, \textit{Military Health System Research Symposium (MHSRS), \textbf{2024}}

\item Celeste Roberts, \textbf{Md. Saif Hassan Onim}, Sanjeev Kumar, Amer M Burhan, Himanshu Thapliyal and Elizabeth K. Rhodus, \say{Implementation of RCT Intervention with Wearable Digital Biometric Collection in Rural Community-residing Dementia Dyads}, \textit{The 19th Annual Spring Conference of the UK Center for Clinical and Translational Science (CCTS), \textbf{2024}}

\end{itemize}
\subsection{Conference Papers}
\begin{itemize}

\item Tyler Cultice, \textbf{Md. Saif Hassan Onim}, Annarita Giani and Himanshu Thapliyal, \say{Anomaly Detection for Real-World Cyber-Physical Security using Quantum Hybrid Support Vector Machine}, \textit{Proceedings of IEEE Computer Society Annual Symposium on VLSI 2024 (ISVLSI 2024), Knoxville, TN, USA, July 1-3, \textbf{2024 (Best Paper Award)}}

\item \textbf{Md. Saif Hassan Onim} and Himanshu Thapliyal, \say{Predicting Stress in Older Adults with RNN and LSTM from Time Series Sensor Data and Cortisol}, \textit{Proceedings of IEEE Computer Society Annual Symposium on VLSI 2024 (ISVLSI 2024), Knoxville, TN, USA, July 1-3, \textbf{2024}}

\item \textbf{Md. Saif Hasan Onim} and Himanshu Thapliyal, \say{CASD-OA: Context-Aware Stress Detection for Older Adults with Machine Learning and Cortisol Biomarker}, \textit{ Proceedings of the Great Lakes Symposium on VLSI 2023 (GLSVLSI 2023), Knoxville, TN, USA. ACM, New York, NY, USA, June 5–7, \textbf{2023}}

\item Md. Akiful Hoque Akif, Koushik Roy, Nawsher Abdullah, Nusrat Zahan Priota and \textbf{Md. Saif Hasan Onim}, \say{Performance Analysis of Machine Learning Models for Cheating Detection in Online Examinations}, \textit{Proceedings of IEEE 25th International Conference on Computer and Information Technology (ICCIT), Cox’s Bazar, Bangladesh, \textbf{2022}}

\item Md Wahiduzzaman Arnob, Arunima Dey Pooja and \textbf{Md. Saif Hasan Onim}, \say{A Combined PCA-MLP Network for Early Breast Cancer Detection}, \textit{Proceedings of 2022 IEEE 2ND Asian Conference on Innovation in Technology (ASIANCON2022), Pune, India, August \textbf{2022}}

\item Tareque Bashar Ovi, Sauda Suara Naba, Dibaloke Chanda and \textbf{Md. Saif Hasan Onim},  \say{A Transfer-Learning Based Ensemble Architecture for ECG Signal Classification}, \textit{Proceedings of  IEEE Region 10 Symposium (TENSYMP2022), Mumbai, India, Jun. \textbf{2022}}

\item Abtahi Ishmam, Mahmudul Hasan, \textbf{Md. Saif Hassan Onim}, Koushik Roy, Md. Akiful Hoque Akif and Hussain Nyeem, \say{Modelling Lips-State Detection Using CNN for Non-Verbal Communications}, \textit{Proceedings of IEEE  International Conference on 4th Industrial Revolution and Beyond (IC4IR), 2021, Dhaka, Bangladesh, \textbf{2021}}

\item Shah Mohazzem Hossain, \textbf{Md. Saif Hasan Onim}, Sagor Biswas and Abdul Hasib Chowdhury, \say{Application of Machine Learning for Optimal Placement of Distributed Generation}, \textit{Proceedings of IEEE  International Conference on Information and Communication Technology for Sustainable Development (ICICT4SD), Dhaka, Bangladesh, pp. 231-234. \textbf{2021}}

\item \textbf{Md. Saif Hasan Onim}, Muhaiminul Islam Akash, Mahmudul Haque and Raiyan Ibne Hafiz, \say{Traffic Surveillance using Vehicle License Plate Detection and Recognition in Bangladesh}, \textit{Proceedings of IEEE International Conference on Electrical and Computer Engineering, pp. 121-124, \textbf{2020}}

\item \textbf{Md. Saif Hassan Onim}, Aiman Rafeed Ehtesham, Amreen Anbar, A. K. M. Nazrul Islam and A. K. M. Mahbubur Rahman, \say{LULC Classification by Semantic Segmentation of Satellite Images Using FastFCN}, \textit{Proceedings of IEEE International Conference on Advanced Information and Communication Technology, pp. 472-476, \textbf{2020}}


\end{itemize}
\subsection{Journals}
\begin{itemize}

\item \textbf{Md. Saif Hassan Onim}, Himanshu Thapliyal and Elizabeth K. Rhodus, \say{Utilizing Machine Learning for Context-Aware Digital Biomarker of Stress in Older Adults} \textit{Information, 15, no. 5: 274, \textbf{2024}}


\item Dibaloke Chanda, \textbf{Md. Saif Hassan Onim}, Hussain Nyeem, Tareque Bashar Ovi, and Sauda Suara Naba, \say{Dcensnet: A New Deep Convolutional Ensemble Network for Skin Cancer Classification}, \textit{Biomedical Signal Processing and Control, vol. 89, p. 105757, \textbf{2024}}

\item \textbf{Md. Saif Hasan Onim}, Himanshu Thapliyal and Elizabeth K. Rhodus \say{A Review of Context-Aware Machine Learning for Stress Detection}, \textit{IEEE Consumer Electronics Magazine, vol. 13, no. 4, pp. 10-16, July \textbf{2024}}

\item \textbf{Md. Saif Hassan Onim}, Hussain Nyeem, Md. Wahiduzzaman Khan Arnob and Arunima Dey Pooja \say{Unleashing the power of generative adversarial networks: A novel machine learning approach for vehicle detection and localisation in the
dark,} \textit{Cognitive Computation and Systems, vol. 5, no. 3, pp. 169–180, \textbf{2023}}.

\item \textbf{Md. Saif Hasan Onim}, Zubayar Mahatab Md Sakif, Adil Ahnaf, Ahsan Kabir, Abul Kalam Azad, Amanullah Maung Than Oo, Rafina Afreen, Sumaita Tanjim Hridy, Mahtab Hossain, Taskeed Jabid and Md Sawkat Ali, \say{Solnet: A Convolutional Neural Network for Detecting Dust on Solar Panels}, \textit{Energies, vol. 16, no. 1, \textbf{2023}}


\item \textbf{Md. Saif Hasan Onim}, Hussain Nyeem, Koushik Roy, Mahmudul Hasan, Abtahi Ishmam, Md. Akiful Hoque Akif, Tareque Bashar Ovi, \say{BLPnet: A new DNN model and Bengali OCR engine for Automatic License Plate Recognition}, \textit{Array, vol. 15, p. 100244, \textbf{2022}}

\end{itemize}

\section{TEACHING \\ EXPERIENCE}
\begin{itemize}
\item Teaching Assistant, Dept of EECS, University of Tennessee, Knoxville (August, 2022-Present)
\item Adjunct Lecturer, Dept. of EECE, Military Institute of Science and Technology (January, 2020-August, 2022)
\item Mentor, Visual Information Processing Research Group, Dept. of EECE, Military Institute of Science and Technology (April, 2021-August, 2022)

\end{itemize}

\section{DISTINCTIONS AND AWARDS}
\begin{itemize}
\item \textbf{2024-present:} Senator, Graduate Student Senate, UTK
\item \textbf{2023-2024:} Outstanding Graduate Teaching Assistant in Computer Engineering, EECS, UTK
\item \textbf{2023-2024:} Publicity and Social Media Officer, Bangladesh Student Association (BSA), University of Tennessee, Knoxville, USA
\item \textbf{2021-present:} Graduate Student Member, Institute of Electrical and Electronics Engineers (IEEE).
\item \textbf{2023-present:} Member, Association for Computing Machinery (ACM).
\item \textbf{2024:} Presentation Chair, ISVLSI'24
\item \textbf{Reviewer:} IEEE TCE, PETI, AJNNA, GLSVLSI, ISVLSI

\end{itemize}
\end{resume}
\end{document}